---
title: "p8105_hw1_yg2762"
author: "Yang Gao"
date: "9/23/2021"
output: github_document
---


# problem 1

## load function
```{r}
library(tidyverse)
```
## create data frame
a random sample of size 10 from a standard Normal distribution;

a logical vector indicating whether elements of the sample are greater than 0;

a character vector of length 10;

a factor vector of length 10, with 3 different factor “levels”.

```{r}
set.seed(1)
problem1_df=
  tibble( 
    norm_samp=rnorm(10),
    norm_samp_pos=norm_samp>0,
    vec_char=c("1","2","3","4","5","6","7","8","9","10"),
    vec_factor=factor(c("1","2","3","2","1","3","1","3","2","1"))
  )
problem1_df
```
## take the mean value
```{r}
mean_samp = mean(pull(problem1_df, norm_samp))
mean_samp

mean_pos=mean(pull(problem1_df, norm_samp_pos))
mean_pos

mean_vec_char=mean(pull(problem1_df, vec_char))

mean_vec_factor=mean(pull(problem1_df,vec_factor))
```
The mean of variable norm_samp is 0.132, the mean of norm_samp_pos is 0.6. The mean of character vector and factor vector cannot be calculated because these two variables are not numeric or logical.

### use code "as numeric"
```{r,eval=FALSE}
pull(problem1_df,norm_samp_pos)
pos_num=as.numeric(problem1_df$norm_samp_pos)
mean(pos_num)

pull(problem1_df,vec_char)
vec_char_num=as.numeric(problem1_df$vec_char)
mean(vec_char_num)
                   
pull(problem1_df,vec_factor)
vec_factor_num=as.numeric(problem1_df$vec_factor)
mean(vec_factor_num)
                  
```
as.numeric function convert elements in vectors into numeric version, so we can calculate the mean. 







